---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcrispr

<!-- badges: start -->

| Master                                        | Develop                                         |
| --------------------------------------------- | ----------------------------------------------- |
| [![Master Badge][circle-master]][circle-base] | [![Develop Badge][circle-develop]][circle-base] |

[![pre-commit](https://img.shields.io/badge/pre--commit-enabled-brightgreen?logo=pre-commit&logoColor=white)](https://github.com/pre-commit/pre-commit)

<!-- badges: end -->

RCRISPR is an R package for single guide CRISPR screen data transformation, analysis and visualisation. It includes functions
for importing count data, calculating log fold changes, generating quality control metrics, parsing MAGeCK and BAGEL results
and producing a variety of summary plots.

RCRISPR forms the basis of the single guide analysis pipeline, [C-SAR](https://github.com/cancerit/C-SAR). Included in RCRISPR
are the scripts run at various stages of the pipeline, allowing them to be used and extended outside of the pipeline.

## Installation

You can install the released version of rcrispr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rcrispr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rcrispr)
## basic example code
```

## Development

### pre-commit

Please install a pre-commit to your user environment (not a venv):

```bash
curl https://pre-commit.com/install-local.py | python3 -
# may need to add to PATH

# in repo folder, enable pre-commit hooks
pre-commit install
```

### Keeping Rmd and md in sync

You should not edit `README.md`, only `README.Rmd`.  Once edited you can update with:

```bash
# native R
r -e 'library(knitr); knit("README.Rmd", "README.md")'

# docker
docker run -ti --rm -v $PWD:/md:rw rocker/r-rmd r -e 'library(knitr); knit("/md/README.Rmd", "/md/README.md")'
```

### Updating licence headers

Please use [skywalking-eyes](https://github.com/apache/skywalking-eyes).

Expected workflow:

```bash
# recent build, change to apache/skywalking-eyes:0.2.0 once released
export DOCKER_IMG=ghcr.io/apache/skywalking-eyes/license-eye@sha256:17a4e86591c9908c8e76531943d5522881a82a33580ad7bdf36938517ef25aa9
```

1. Check state before modifying `.licenserc.yaml`:
   - `docker run -it --rm -v $(pwd):/github/workspace $DOCKER_IMG header check`
   - You should get some 'valid' here, those without a header as 'invalid'
1. Modify `.licenserc.yaml`
1. Apply the changes:
   - `docker run -it --rm -v $(pwd):/github/workspace $DOCKER_IMG header fix`
1. Add/commit changes

The check is executed in the CI pipeline which will fail if expected files are missing the license.

*DO NOT* edit the header in the files, please modify the date component of `content` in `.licenserc.yaml`.  The only files needing manual update being:

- `README.Rmd`

If you need to make more extensive changes to the license carefully test the pattern is functional.

## LICENSE

```
Copyright (c) 2021 Genome Research Ltd

Author: CASM/Cancer IT <cgphelp@sanger.ac.uk>

This file is part of RCRISPR.

This program is free software: you can redistribute it and/or modify
it under the terms of the GNU Affero General Public License as
published by the Free Software Foundation, either version 3 of the
License, or (at your option) any later version.

This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU Affero General Public License for more details.

You should have received a copy of the GNU Affero General Public License
along with this program.  If not, see <https://www.gnu.org/licenses/>.

1. The usage of a range of years within a copyright statement contained within
this distribution should be interpreted as being equivalent to a list of years
including the first and last year specified and all consecutive years between
them. For example, a copyright statement that reads ‘Copyright (c) 2005, 2007-
2009, 2011-2012’ should be interpreted as being identical to a statement that
reads ‘Copyright (c) 2005, 2007, 2008, 2009, 2011, 2012’ and a copyright
statement that reads ‘Copyright (c) 2005-2012’ should be interpreted as being
identical to a statement that reads ‘Copyright (c) 2005, 2006, 2007, 2008,
2009, 2010, 2011, 2012’.
```

<!-- References -->

[circle-develop]: https://circleci.com/gh/cancerit/RCRISPR.svg?style=shield&branch=dev%3B
[circle-master]: https://circleci.com/gh/cancerit/RCRISPR.svg?style=shield&branch=master%3B
[circle-repo]: https://app.circleci.com/pipelines/github/cancerit/RCRISPR
[circle-base]: https://circleci.com/gh/cancerit/RCRISPR.svg?style=shield
